ABC Group Level Fits

### 2024-01-11 Model/abc_hier.qmd
summary stat version of indv fits

  train_mean_rmse <- sqrt(mean((sum_stat$mean_dif^2)))
  train_sd_rmse <- sqrt(mean((sum_stat$sd_dif^2)))

  test_mean_rmse <- sqrt(mean((sum_stat_test$mean_dif^2)))
  test_sd_rmse <- sqrt(mean((sum_stat_test$sd_dif^2)))

  return(tibble::lst(train_mean_rmse,test_mean_rmse))

>>>>

  train_mean_rmse <- sqrt(mean((sum_stat$mean_dif^2)))
  train_sd <- mean(sum_stat_train$sd_obs)

  test_mean_rmse <- sqrt(mean((sum_stat_test$mean_dif^2)))
  test_sd <- mean(sum_stat_test$sd_obs)

  return(tibble::lst(train_mean_rmse,test_mean_rmse, train_sd, test_sd))
